---
title: "Getting started with binomial package"
author: "Qiming Wu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{binomial-package-intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Binomial Distribution Package Overview

The package `"binomial"` implements functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc. It also provides some visualizations and summary for the binomial distribution.

## Getting Started

First, load the package with the following command in the console.
```{r}
library(binomial)
```

There are a few _main_ functions for direct use.  
1. `bin_choose` calculates the number of combinations to get `k` successes from `n` trials.

```{r}
bin_choose(n = 10, k = 5)
```

2. `bin_probability` calculates the probability of getting `k` successes from `trials` with success probability `prob`.

```{r}
bin_probability(success = 5, trials = 10, prob = 0.5)
```

3. `bin_distribution` displays a data frame containing the probability distribution information. You can also bar plot of the distribution with `plot()` method.

```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
dis1
plot(dis1)
```

4. `bin_cumulative` extends `bin_distribution` by another column, containing the cumulative distribution for binomial variables. You can also plot the cumulative distribution with `plot()` method.

```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
dis2
plot(dis2)
```

5. `bin_variable` creates a binomial variable object. You can get some summary statistics using `summary()` method.

```{r}
bin_var <- bin_variable(trials = 5, prob = 0.5)
bin_var
```

```{r}
var_summary <- summary(bin_var)
var_summary
```

There are five summary statistics supported by this package:

Assume a random variable $X$ follows $Bin(n, p)$ distribution.

- Mean $E(X) = np$
- Variance $Var(X) = np(1-p)$
- Mode $Mode(X) = int(np + p)$
- Skewness $skewness = \frac{1 - 2p}{\sqrt{np(1-p)}}$
- Kurtosis $kurtosis = \frac{1 - 6p(1 - p)}{np(1 - p)}$

6. You can calculates each summary statistic independently by calling the corresponding functions with number of trials and probability of success.

```{r}
bin_mean(trials = 5, prob = 0.5)
bin_variance(trials = 5, prob = 0.5)
bin_mode(trials = 5, prob = 0.5)
bin_skewness(trials = 5, prob = 0.5)
bin_kurtosis(trials = 5, prob = 0.5)
```

All _main_ functions mentioned above are internally supported by _private_ auxilary functions that do all actual computations. These functions are NOT intended to be called directly by the user.

## Getting Help

If you need additional help with functions in the package, please consult documentations for concrete explanantions and examples.

For example, if you would like to know more about calculating binomial probabilities using bin_probability(), use one of the following two ways to get help:

```{r eval=FALSE}
?bin_probability
help(bin_probability)
```

---
