---
title: "Getting started with binomial package"
author: "Qiming Wu"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{binomial-package-intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(binomial)
```

## Binomial Distribution

The package `"binomial"` implements functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc. It also provides some visualizations and summary for the binomial distribution.

## Package Structures

There are a few _main_ functions for direct use.  
1. `bin_choose` calculates the number of combinations to get `k` successes from `n` trials.
```{r eval = FALSE}
bin_choose(n, k)
```

2. `bin_probability` calculates the probability of getting `k` successes from `trials` with success probability `prob`.
```{r eval = FALSE}
bin_probability(success, trials, prob)
```

3. `bin_distribution` displays a data frame containing the probability distribution information. You can also bar plot of the distribution with `plot()` method.
```{r eval = FALSE}
dis1 <- bin_distribution(trials, prob)
dis1
plot(dis1)
```

4. `bin_cumulative` extends `bin_distribution` by another column, containing the cumulative distribution for binomial variables. You can also plot the cumulative distribution with `plot()` method.
```{r eval = FALSE}
dis2 <- bin_cumulative(trials, prob)
dis2
plot(dis2)
```

5. `bin_variable` creates a binomial variable object. You can get some summary statistics using `summary()` method.

There are five summary statistics supported by this package:

Assume a random variable $X$ follows $Bin(n, p)$ distribution.

- Mean $E(X) = np$
- Variance $Var(X) = np(1-p)$
- Mode $Mode(X) = int(np + p)$
- Skewness $skewness = \frac{1 - 2p}{\sqrt{np(1-p)}}$
- Kurtosis $kurtosis = \frac{1 - 6p(1 - p)}{np(1 - p)}$

You can calculates this measures independently by calling the corresponding functions.
```{r eval=FALSE}
bin_mean()
bin_variance()
bin_mode()
bin_skewness()
bin_kurtosis()
```

All _main_ functions mentioned above are internally supported by _private_ auxilary functions. These functions are NOT intended to be called directly by the user.

---
